\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{Acknowledgments}
\chapter*{ACKNOWLEDGMENTS}

\begin{small}
At the beginning of this work and before any development, it seems appropriate to thank first of all, Sanlam Pan Africa Group, for the opportunity it gave us to do our end of study internship at the \acrfull{df}, the digital pole of its Moroccan subsidiary Saham Assurance. We were welcomed by a wonderful, available and enthusiastic team. We would like to thank the members of the "Data" team for their availability; in particular, Mr. \textbf{JAMAL-BENNIS Zouhair} Agile Coach and Mrs. \textbf{SADIKI Fatimaezzahra} Data Engineer for their supervision and monitoring. We do not forget all the staff of Colina Participations who received us in an environment full of sympathy and good humor, which contributed to facilitate our integration. A special thanks to Mrs. \textbf{KADIA Essan}, Mr. \textbf{KOUASSI Dhom} and all the HR team for their kindness and contribution to the realization of this work.  \\

We thank Orange Group, the X Polytechnic Foundation, the X Polytechnic School of Paris, the \acrfull{inp} of Yamoussoukro and the \acrfull{ensea} of Abidjan who have done everything possible for the success of this training and continue to work on it. We also express our deep gratitude to the administration of \acrshort{inp}, in particular to Mr. \textbf{KOFFI N'Guéssan}  the former director general of \acrlong{inp}, \textbf{Dr. TANOH Lambert}, Director of the \acrshort{idsi}, to the teaching and administrative staff including \textbf{Dr. KADJO Lambert}, the Academic Director of \acrshort{idsi} and \textbf{Miss SORO Chantal} the executive assistant of \acrshort{idsi}. Our most distinguished thanks also go to our pedagogical supervisor, Professor \textbf{BROU Konan Marcellin} for having followed our work with diligence and rigor. 
\\

Finally, we would like to thank our fellow students of the $3^{rd}$ class of \acrshort{idsi}, our parents, brothers and sisters who have supported us morally and financially throughout this training. We express our deep respect to all those who took their time to read and correct this thesis.

\end{small}
%La rédaction de ce mémoire a été un travail de concert avec des personnes de bonne volonté qui nous ont soutenu et accompagné. ter
